---
title: "MixedEffectsCPETmodels"
author: "nickcoronato"
date: "2021-07-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r load libraries, echo = FALSE}
# Call the appropriate libraries.
library(tidyverse)
library(plyr)
library(dplyr)
library(splines)
library(boot)
library(broom)
library(lme4)
library(lmerTest)
library(jtools)
library(devtools)
library(lattice)
library(fifer)
library(flexplot)
library(sjPlot)
library(officer)
library(flextable)
library(lsmeans)
library(effects)
library(ggiraph)
library(ggiraphExtra)
library(ggeffects)
library(emmeans)
library(performance)
```
```{r options1}
options(max.print=99999)
control=lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4))
```

# Data preparation

## Read in the csv of clean data, from this project's "Data" folder.
```{r Read in data, message = FALSE, include = FALSE}
here::i_am("analysis/MixedEffectsCPETmodels.Rmd")
library(here)

all_GK_raw  <-  read_delim(here("data","all_data.csv"),"," ) #This is the raw data set

# This next step divides the full time series for each subject into their 5-10 Exercise and Recovery bouts. Bouts labelled with a ".5" suffix are the recovery (off-transient) bouts.

all_GK_bybout <- mutate(all_GK_raw, 
                        bout =case_when(
  (Time_Sec<120 & Work < 10)~"0",
  (Time_Sec >= 2 & Time_Sec < 175 & Work >=10)~"1",
  (Time_Sec<185 & Work < 10)~"1.5",
  (Time_Sec >= 175 & Time_Sec<300 & Work >=10)~"2",
  (Time_Sec<365 & Work < 10)~"2.5",
  (Time_Sec >= 300 & Time_Sec < 495 & Work >=10)~"3",
  (Time_Sec<545 & Work < 10)~"3.5",
  (Time_Sec >= 495 & Time_Sec <675 & Work >=10)~"4",
  (Time_Sec<725 & Work < 10)~"4.5",
  (Time_Sec >= 675 & Time_Sec <855 & Work >=10)~"5",
  (Time_Sec<905 & Work < 10)~"5.5", 
  (Time_Sec >= 855 & Time_Sec <1035 & Work >= 10)~"6", 
  (Time_Sec<1085 & Work < 10)~"6.5", 
  (Time_Sec >= 1035 & Time_Sec <1215 & Work >= 10)~"7", 
  (Time_Sec<1265 & Work < 10)~"7.5",
  (Time_Sec >= 1215 & Time_Sec <1400 & Work >= 10)~"8", 
  (Time_Sec <1445 & Work < 10)~"8.5",
  (
    # Time_Sec >= 1400 & 
      Time_Sec <1575 & Work >= 10)~"9",
  (
    # Time_Sec >= 1540 & 
     Time_Sec<1625 & Work < 10)~"9.5",
  (Time_Sec >= 1575 & Work >= 10)~"10", 
  (Time_Sec >= 1625 & Work < 10)~"10.5"))

names(all_GK_bybout)[13] <- "Tanner"
# 'Tanner' column is the descriptor for the puberty variable. Early pubertal subjects score 1-2 on the Tanner scale, and late pubertal subjects score 4-5.

# The next step ensures that we have all variables of interest. Note that some are normalized by bodymass (kg) and lean body mass (kg), which are slightly different measurements.
all_GK_bybout <- mutate(all_GK_bybout, "VO2/kglbm"=VO2 / lbm,"VE/VCO2" = (VE / VCO2),"VCO2/kg" =  VCO2/bodymass,"VE/kg" = VE/bodymass, "VCO2/kglbm" =  VCO2/lbm,"VE/kglbm" = VE/lbm)


# All variables should be coded as Factors, with the exception of bout, which is our discrete repeated measure.
all_GK_bybout$Tanner <- as.factor(all_GK_bybout$Tanner)
all_GK_bybout$Gender <- as.factor(all_GK_bybout$Gender)
all_GK_bybout$intensity <- as.factor(all_GK_bybout$intensity)
# all_GK_bybout$bout <- as.factor(all_GK_bybout$bout)
all_GK_bybout$ID <- as.factor(all_GK_bybout$ID)


all_GK_bybout <- all_GK_bybout %>% dplyr::select(ID, bodymass, lbm, intensity, Tanner, Gender, bout, Time_Sec, Work, HR, VO2, 'VO2/kg', 'VO2/kglbm', VCO2, 'VCO2/kg', 'VCO2/kglbm', RQ, VE, 'VE/kg','VE/kglbm', RR, `VE/VCO2`)
all_GK_bybout <- as_tibble(all_GK_bybout)

head(all_GK_bybout,6)

# Check for any NA values in bout column.
(extra_NA <- all_GK_bybout[is.na(all_GK_bybout$bout),])

(summary(all_GK_bybout)) 
```

Create a 'demographics' table for later use, which contains the listing of IDs used in the models.
```{r create demographics}
demographics <- distinct(all_GK_bybout, ID, .keep_all=TRUE)[,1:6]
```

## Convert the 'bout' variable to discrete numeric values. For the off-transient bouts (recovery periods), subtract 1.5 in order to center the variable at 0 for further analysis.
```{r Convert bout var, message=FALSE, warning=FALSE}
ontransbouts <- filter(all_GK_bybout,bout%in%c(0,1,2,3,4,5))
ontransbouts$bout <- as.numeric(ontransbouts$bout)

offtransbouts <- filter(all_GK_bybout,bout%in%c(1.5,2.5,3.5,4.5,5.5,6.5))
offtransbouts$bout <- as.numeric(offtransbouts$bout)
offtransbouts <- mutate(offtransbouts, bout = bout-1.5)
```

## Compute the averages. Pull out the 'avgHR' at each "on-transient" and "off-transient" bout (1-5).
```{r compute avgHR}
avgHRon <- aggregate(ontransbouts$HR, by=list(bout=ontransbouts$bout, ID = ontransbouts$ID, intensity = ontransbouts$intensity, Gender=ontransbouts$Gender, Tanner=ontransbouts$Tanner), FUN=mean) 
names(avgHRon)[6] <- "avgHR"

avgHRoff <- aggregate(offtransbouts$HR, by=list(bout=offtransbouts$bout, ID = offtransbouts$ID, intensity = offtransbouts$intensity, Gender=offtransbouts$Gender, Tanner=offtransbouts$Tanner), FUN=mean)
names(avgHRoff)[6] <- "avgHR"
```

## Data visualization. Plot the average HR data distributions.
```{r plot avgHR}
# plot the avg ON-transient HR
ggplot(data=avgHRon, aes(bout, avgHR, color = intensity)) + geom_point() + ggtitle("On-Transient average heart rates")

# plot the avg off-transient HR
ggplot(data=avgHRoff, aes(bout, avgHR, color = intensity)) + geom_point()+ ggtitle("Off-Transient average heart rates")

ggplot(data=filter(avgHRon, intensity == "low"), aes(x = bout,y= avgHR, group = ID)) + geom_line() + ggtitle("Low intensity, Avg HR for on-transient periods")+ ylim(80,210) 

ggplot(data=filter(avgHRoff, intensity == "low"), aes(x = bout,y= avgHR, group = ID)) + geom_line() + ggtitle("Low intensity, Avg HR for off-transient periods")+ ylim(80,210)

ggplot(data=filter(avgHRon, intensity == "high"), aes(x = bout,y= avgHR, group = ID)) + geom_line() + ggtitle("High intensity, Avg HR for on-transient periods") + ylim(80,210) 

ggplot(data=filter(avgHRoff, intensity == "high"), aes(x = bout,y= avgHR, group = ID)) + geom_line() + ggtitle("High intensity, Avg HR for off-transient periods") + ylim(80,210)
```

### Show xyplots to compare the slopes for each individual based on Gender, Tanner score, intensity
```{r xyplot avgHR}
xyplot(avgHR ~ bout | Gender*Tanner, data = avgHRon, groups = intensity, 
       type = c("p","r"), 
       auto.key = TRUE)

xyplot(avgHR ~ bout | ID, data = avgHRon, groups = Tanner, type = c("p","r"), auto.key = TRUE)

xyplot(avgHR ~ bout | ID, data = avgHRon, groups = intensity, type = c("p","r"), auto.key = TRUE)
```

### More visualizations
```{r boxplot avgHR}
boxplot(avgHR~Gender*Tanner*bout*intensity, data = avgHRon)
```

```{r flexplot avgHR}
### Viewing the categorical variables of interest

# Flexplot of Gender distribution
flexplot(avgHR~Gender, data=avgHRon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgHR~Gender, data=avgHRoff, spread="quartiles", jitter=c(.1, 0))

# Flexplot of Puberty distribution
flexplot(avgHR~Tanner, data=avgHRon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgHR~Tanner, data=avgHRoff, spread="quartiles", jitter=c(.1, 0))


### show a straight line, remove standard errors, and specify 2 bins
flexplot(avgHR~bout + intensity | Gender + Tanner, data=avgHRon, method="lm", se=F, bins=2)

### multivariate relationship (this is more data exploration, prior to the real modeling.)
flexplot(avgHR~bout + intensity | Gender + Tanner, data=avgHRon)
flexplot(avgHR~bout + Gender | intensity + Tanner, data=avgHRon)
flexplot(avgHR~bout + Tanner | intensity + Gender, data=avgHRon)
```


#################################################

# LINEAR MIXED EFFECTS MODELING with the lme4 package
This next section is the full procedure for step-wise variable selection to identify the appropriate mixed-effects model.

In total, there are 14 selected models. Each physiological signal (x7) has two associated models: one linear model is fit to the On-Transient average responses, and a second model is fit to the Off-Transient averages. 

The final multi-level models (MLMs) were chosen through a stepwise variable selection approach that began with the most complex model. Fixed effects considered in the full model were: 
Gender, a factor with two levels (Male, Female); 
Maturational status, a factor with two levels (Early, Late); 
work intensity, a factor with two levels (Low, High); 
and Bout, a continuous predictor in the range of 0 to 5. 

Random slope and intercept were allowed in the bout term for each participant ID in order to account for individual variation between subjects. This controlled for innate differences between subjects’ physical fitness levels, psychological motivation, and other non-measured variables. If the full model showed insignificance (p-value > 0.05) in the four-way interaction (Gender* Puberty * Intensity * Bout), the model was re-fit with only three-way interactions. 

This stepwise process was repeated, removing higher-level interactions until all fixed effects were statistically significant or no more interactions existed. In order to determine that a simpler model provided better fit than the previous (more complex) model, a standard ANOVA process and Chi-squared comparison was used, as well as a check for reduction in BIC and a Bayes Factor analysis. The simplest possible models used only fixed effects for Gender, Puberty, Intensity, and Bout. However, each of the final 14 models included a unique combination of fixed effects and cross-level interactions that required careful interpretation. Residual plots were analyzed for each final model to confirm an appropriate fit.

The first physiological signal for analysis is Heart Rate (HR).

## HR ON Transient

### Null Model
The null model does not use any predictor variables from the other levels (Gender, Tanner, intensity, bout). This is also considered the "intercept only" model.
```{r}
nullmod <- lmer(avgHR ~ 1 + (1|ID), data = avgHRon, REML = TRUE)
(summ(nullmod) ->summnullHRon)
(BIC(nullmod) -> BICnullHRon)
(summnullHRon$gvars[,3] -> ICCnullHRon)
```

### Model 1: All interactions
The intermediate model uses all predictor variables and their interactions (Gender, Tanner, intensity, bout) with a random slope.
```{r m1 HRon}
intHRon <- lmer(avgHR~Gender*Tanner*intensity*bout +(bout|ID), data = avgHRon, REML=FALSE)
# summary(intHRon)
(summ(intHRon)->summintHRon)
(BIC(intHRon) -> BICintHRon)
(summintHRon$gvars[,3] -> ICCintHRon)
# coef(intHRon)
# fixef(intHRon)
# ranef(intHRon)
```

### Model 1B: Some interactions
The final model uses a subset of the predictor variables; the three-way interaction of Tanner:Bout:Intensity is the highest-level interaction with reported significance level p<=0.05. Model 1B becomes the final model for on-transient HR, 'HRon'.
```{r m1B HRon}
HRon <- lmer(avgHR~Gender + Tanner * bout * intensity + (bout|ID)  , data = avgHRon, REML=FALSE)
# summary(HRon)
# coef(HRon)
# ranef(HRon)
(summ(HRon)->summHRon)
(BIC(HRon) -> BICHRon)
(summHRon$gvars[,3] -> ICCHRon)
```

### Comparing On transient models
```{r compare HRon}
improve.fit(HRon,intHRon)
anova(HRon, intHRon)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r HRoncoefs}
HRoncoefs <- as_tibble(coef(HRon)$ID)

HRoncoefs <- tibble(demographics, HRoncoefs$bout)

write.csv(HRoncoefs,"~/R/MBEB-CPET/output/HRoncoefs.csv", row.names = TRUE)
```


## HR OFF transient
### Null Model
The null model does not use any predictor variables from the other levels (Gender, Tanner, intensity, bout). This is also considered the "intercept only" model.
```{r}
nullmod <- lmer(avgHR ~ 1 + (1|ID), data = avgHRoff, REML = TRUE)
(summ(nullmod) ->summnullHRoff)
(BIC(nullmod) -> BICnullHRoff)
(summnullHRoff$gvars[,3] -> ICCnullHRoff)
```

### Model 2: OFF TRANSIENT: All interactions

```{r m2 HRoff}
intHRoff <- lmer(avgHR~Gender*Tanner*bout*intensity + (bout|ID)  , data = avgHRoff, REML=FALSE)
# summary(intHRoff)
(summ(intHRoff)->summintHRoff)
(BIC(intHRoff) -> BICintHRoff)
(summintHRoff$gvars[,3] -> ICCintHRoff)
# coef(intHRoff)
# ranef(intHRoff)
```

### Model 2C: Some interactions
```{r m2c HRoff}
HRoff <- lmer(avgHR~ bout * intensity + Tanner*intensity + Gender*intensity + (bout|ID)  ,  data = avgHRoff, REML=FALSE)
# summary(intHRoff)
(summ(HRoff)->summHRoff)
(BIC(HRoff) -> BICHRoff)
(summHRoff$gvars[,3] -> ICCHRoff)
# coef(intHRoff)
# fixef(intHRoff)
# ranef(intHRoff)
```

### Comparing Off transient models
```{r compare HRoff}
improve.fit(HRoff,intHRoff)
anova(HRoff, intHRoff)
```
```{r bayes factor HRoff}
# Bayes factor = probability of full model / probability of reduced model - it's an odds. We can approximate BF using BIC:
# in general, BF >10 = strong evidence in favor of the model in the numerator
bf.bic(HRoff,intHRoff)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r HRoff coefs}
HRoffcoefs <- as_tibble(coef(HRoff)$ID)

HRoffcoefs <- tibble(demographics, HRoffcoefs$bout)

write.csv(HRoffcoefs,"~/R/MBEB-CPET/output/HRoffcoefs.csv", row.names = TRUE)
```

## VO2/kg LEAN BODY MASS On Transient

First, pull out the average on and off transient VO2kg values for each bout.
```{r compute vo2kglbm avg}
avgVO2kglbmon <- aggregate(ontransbouts$'VO2/kg', by=list(bout=ontransbouts$bout, ID = ontransbouts$ID, intensity = ontransbouts$intensity, Gender=ontransbouts$Gender, Tanner=ontransbouts$Tanner), FUN=mean) 
names(avgVO2kglbmon)[6] <- "avgVO2kglbm"

avgVO2kglbmoff <- aggregate(offtransbouts$'VO2/kg', by=list(bout=offtransbouts$bout, ID = offtransbouts$ID, intensity = offtransbouts$intensity, Gender=offtransbouts$Gender, Tanner=offtransbouts$Tanner), FUN=mean)
names(avgVO2kglbmoff)[6] <- "avgVO2kglbm"
```


### Plot the average VO2kglbm data distributions.
```{r plot vo2kglbm}
#plot the avg ON-transient VO2kglbm
ggplot(data=avgVO2kglbmon, aes(bout, avgVO2kglbm, color = intensity)) + geom_point() + ggtitle("On-Transient average VO2/kg rates")

#plot the avg off-transient VO2kglbm
ggplot(data=avgVO2kglbmoff, aes(bout, avgVO2kglbm, color = intensity)) + geom_point()+ ggtitle("Off-Transient average VO2/kg rates")

ggplot(data=filter(avgVO2kglbmon, intensity == "low"), aes(x = bout,y= avgVO2kglbm, group = ID)) + geom_line() + ggtitle("Low intensity, Avg VO2kglbm for on-transient periods") + ylim(0,75) 
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgVO2kglbmoff, intensity == "low"), aes(x = bout,y= avgVO2kglbm, group = ID)) + geom_line() + ggtitle("Low intensity, Avg VO2kglbm for off-transient periods")+  ylim(0,75) 

ggplot(data=filter(avgVO2kglbmon, intensity == "high"), aes(x = bout,y= avgVO2kglbm, group = ID)) + geom_line() + ggtitle("High intensity, Avg VO2kglbm for on-transient periods")  + ylim(0,75) 
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgVO2kglbmoff, intensity == "high"), aes(x = bout,y= avgVO2kglbm, group = ID)) + geom_line() + ggtitle("High intensity, Avg VO2kglbm for off-transient periods") + ylim(0,75)  
```

### Show xyplots to compare the slopes for each individual based on Gender, Tanner score, intensity
```{r xyplot vo2kglbm}
xyplot(avgVO2kglbm ~ bout | ID, data = avgVO2kglbmon, groups = Gender, type = c("p","r"), auto.key = TRUE)

xyplot(avgVO2kglbm ~ bout | ID, data = avgVO2kglbmon, groups = Tanner, type = c("p","r"), auto.key = TRUE)

xyplot(avgVO2kglbm ~ bout | ID, data = avgVO2kglbmon, groups = intensity, type = c("p","r"), auto.key = TRUE)
```

### More visualizations
```{r flexplot vo2kglbm}
### categorical variable
flexplot(avgVO2kglbm~Gender, data=avgVO2kglbmon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgVO2kglbm~Gender, data=avgVO2kglbmoff, spread="quartiles", jitter=c(.1, 0))

flexplot(avgVO2kglbm~Tanner, data=avgVO2kglbmon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgVO2kglbm~Tanner, data=avgVO2kglbmoff, spread="quartiles", jitter=c(.1, 0))

### show a straight line, remove standard errors, and specify 2 bins
flexplot(avgVO2kglbm~bout + intensity | Gender + Tanner, data=avgVO2kglbmon, method="lm", se=F, bins=2)

### multivariate relationship
flexplot(avgVO2kglbm~bout + intensity | Gender + Tanner, data=avgVO2kglbmon)
flexplot(avgVO2kglbm~bout + Gender | intensity + Tanner, data=avgVO2kglbmon)
flexplot(avgVO2kglbm~bout + Tanner | intensity + Gender, data=avgVO2kglbmon)
```



### Null Model
```{r}
nullmod <- lmer(avgVO2kglbm ~ 1 + (1|ID), data = avgVO2kglbmon, REML = TRUE)
(summ(nullmod) ->summnullVO2KGLBMon)
(BIC(nullmod) -> BICnullVO2KGLBMon)
(summnullVO2KGLBMon$gvars[,3] -> ICCnullVO2KGLBMon)
```
### Model 1: All interactions

```{r m1 vo2kglbmon}
intVO2KGLBMon <- lmer(avgVO2kglbm~Gender*Tanner*bout*intensity +(bout|ID) , data = avgVO2kglbmon, REML=FALSE)
# summary(intVO2KGLBMon)
(summ(intVO2KGLBMon)->summintVO2KGLBMon)
(BIC(intVO2KGLBMon) -> BICintVO2KGLBMon)
(summintVO2KGLBMon$gvars[,3] -> ICCintVO2KGLBMon)
# coef(intVO2KGLBMon)
# fixef(intVO2KGLBMon)
# ranef(intVO2KGLBMon)
```

### Model 1C: Some interactions

```{r m1c vo2kglbmon}
VO2KGLBMon <- lmer(avgVO2kglbm~ bout*intensity + Gender* intensity + Tanner + (bout|ID) , data = avgVO2kglbmon, REML=FALSE)
# summary(VO2KGLBMon)
# coef(VO2KGLBMon)
# ranef(VO2KGLBMon)
(summ(VO2KGLBMon)->summVO2KGLBMon)
(BIC(VO2KGLBMon) -> BICVO2KGLBMon)
(summVO2KGLBMon$gvars[,3] -> ICCVO2KGLBMon)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r vo2kglbmon coefs}
VO2oncoefs <- as_tibble(coef(VO2KGLBMon)$ID)

VO2oncoefs <- tibble(demographics, VO2oncoefs$bout)

write.csv(VO2oncoefs,"~/R/MBEB-CPET/output/VO2oncoefs.csv", row.names = TRUE)
```

## VO2kglbm OFF TRANSIENT

### Null Model
```{r}
nullmod <- lmer(avgVO2kglbm ~ 1 + (1|ID), data = avgVO2kglbmoff, REML = TRUE)
(summ(nullmod) ->summnullVO2KGLBMoff)
(BIC(nullmod) -> BICnullVO2KGLBMoff)
(summnullVO2KGLBMoff$gvars[,3] -> ICCnullVO2KGLBMoff)
```

### Model 2: All interactions

```{r m2 vo2kglbmoff}
intVO2KGLBMoff <- lmer(avgVO2kglbm~Gender*Tanner*bout*intensity +(bout|ID) ,data = avgVO2kglbmoff, REML=FALSE)
# summary(intVO2KGLBMoff)
(summ(intVO2KGLBMoff)->summintVO2KGLBMoff)
(BIC(intVO2KGLBMoff) -> BICintVO2KGLBMoff)
(summintVO2KGLBMoff$gvars[,3] -> ICCintVO2KGLBMoff)
# coef(intVO2KGLBMoff)
# fixef(intVO2KGLBMoff)
# ranef(intVO2KGLBMoff)
```

### Model 2C: Some interactions
```{r m2c vo2kglbmoff}
VO2KGLBMoff <- lmer(avgVO2kglbm~ bout*intensity + Gender*intensity + Tanner*intensity + (bout|ID) , data = avgVO2kglbmoff, REML=FALSE)
# summary(VO2KGLBMoff)
# coef(VO2KGLBMoff)
# ranef(VO2KGLBMoff)
(summ(VO2KGLBMoff)->summVO2KGLBMoff)
(BIC(VO2KGLBMoff) -> BICVO2KGLBMoff)
(summVO2KGLBMoff$gvars[,3] -> ICCVO2KGLBMoff)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r vo2kglbmoff coefs}
VO2offcoefs <- as_tibble(coef(VO2KGLBMoff)$ID)

VO2offcoefs <- tibble(demographics, VO2offcoefs$bout)

write.csv(VO2offcoefs,"~/R/MBEB-CPET/output/VO2offcoefs.csv", row.names = TRUE)
```

## VCO2/kg lean body mass On Transient

First, pull out the average on and off transient VCO2kglbm values for each bout.
```{r compute VCO2kglbm avg}
avgVCO2kglbmon <- aggregate(ontransbouts$'VCO2/kglbm', by=list(bout=ontransbouts$bout, ID = ontransbouts$ID, intensity = ontransbouts$intensity, Gender=ontransbouts$Gender, Tanner=ontransbouts$Tanner), FUN=mean) 
names(avgVCO2kglbmon)[6] <- "avgVCO2kglbm"

avgVCO2kglbmoff <- aggregate(offtransbouts$'VCO2/kglbm', by=list(bout=offtransbouts$bout, ID = offtransbouts$ID, intensity = offtransbouts$intensity, Gender=offtransbouts$Gender, Tanner=offtransbouts$Tanner), FUN=mean)
names(avgVCO2kglbmoff)[6] <- "avgVCO2kglbm"
```

### Plot the average VCO2kglbm data distributions.
```{r plot VCO2kglbm}
#plot the avg ON-transient VCO2kglbm
ggplot(data=avgVCO2kglbmon, aes(bout, avgVCO2kglbm, color = intensity)) + geom_point() + ggtitle("On-Transient average VO2/kg rates")

#plot the avg off-transient VCO2kglbm
ggplot(data=avgVCO2kglbmoff, aes(bout, avgVCO2kglbm, color = intensity)) + geom_point()+ ggtitle("Off-Transient average VCO2kglbm rates")

ggplot(data=filter(avgVCO2kglbmon, intensity == "low"), aes(x = bout,y= avgVCO2kglbm, group = ID)) + geom_line() + ggtitle("Low intensity, Avg VCO2kglbm for on-transient periods") + ylim(0,0.2) 
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgVCO2kglbmoff, intensity == "low"), aes(x = bout,y= avgVCO2kglbm, group = ID)) + geom_line() + ggtitle("Low intensity, Avg VCO2kglbm for off-transient periods")+  ylim(0,0.2)

ggplot(data=filter(avgVCO2kglbmon, intensity == "high"), aes(x = bout,y= avgVCO2kglbm, group = ID)) + geom_line() + ggtitle("High intensity, Avg VCO2kglbm for on-transient periods")  + ylim(0,0.2)
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgVCO2kglbmoff, intensity == "high"), aes(x = bout,y= avgVCO2kglbm, group = ID)) + geom_line() + ggtitle("High intensity, Avg VCO2kglbm for off-transient periods") + ylim(0,0.2)
```

### Show xyplots to compare the slopes for each individual based on Gender, Tanner score, intensity
```{r xyplot VCO2kglbm}
xyplot(avgVCO2kglbm ~ bout | ID, data = avgVCO2kglbmon, groups = Gender, type = c("p","r"), auto.key = TRUE)

xyplot(avgVCO2kglbm ~ bout | ID, data = avgVCO2kglbmon, groups = Tanner, type = c("p","r"), auto.key = TRUE)

xyplot(avgVCO2kglbm ~ bout | ID, data = avgVCO2kglbmon, groups = intensity, type = c("p","r"), auto.key = TRUE)
```

### More visualizations
```{r flexplot VCO2kglbm}
### categorical variable
flexplot(avgVCO2kglbm~Gender, data=avgVCO2kglbmon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgVCO2kglbm~Gender, data=avgVCO2kglbmoff, spread="quartiles", jitter=c(.1, 0))

flexplot(avgVCO2kglbm~Tanner, data=avgVCO2kglbmon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgVCO2kglbm~Tanner, data=avgVCO2kglbmoff, spread="quartiles", jitter=c(.1, 0))

### show a straight line, remove standard errors, and specify 2 bins
flexplot(avgVCO2kglbm~bout + intensity | Gender + Tanner, data=avgVCO2kglbmon, method="lm", se=F, bins=2)

### multivariate relationship
flexplot(avgVCO2kglbm~bout + intensity | Gender + Tanner, data=avgVCO2kglbmon)
flexplot(avgVCO2kglbm~bout + Gender | intensity + Tanner, data=avgVCO2kglbmon)
flexplot(avgVCO2kglbm~bout + Tanner | intensity + Gender, data=avgVCO2kglbmon)
```


### Null Model
```{r}
nullmod <- lmer(avgVCO2kglbm ~ 1 + (1|ID), data = avgVCO2kglbmon, REML = TRUE)
(summ(nullmod) ->summnullVCO2kglbmon)
(BIC(nullmod) -> BICnullVCO2kglbmon)
(summnullVCO2kglbmon$gvars[,3] -> ICCnullVCO2kglbmon)
```

### Model 1: All interactions

```{r m1 VCO2kglbmon}
intVCO2kglbmon <- lmer(avgVCO2kglbm~bout*intensity*Gender*Tanner +(bout|ID)  , data = avgVCO2kglbmon, REML=FALSE)
# summary(intVCO2kglbmon)
(summ(intVCO2kglbmon)->summintVCO2kglbmon)
(BIC(intVCO2kglbmon) -> BICintVCO2kglbmon)
(summintVCO2kglbmon$gvars[,3] -> ICCintVCO2kglbmon)
# coef(intVCO2kglbmon)
# fixef(intVCO2kglbmon)
# ranef(intVCO2kglbmon)
```

### Model 1B: Some interactions

```{r m1b VCO2kglbmon}
VCO2kglbmon <- lmer(avgVCO2kglbm~ Gender + Tanner*bout + Tanner*intensity + Gender*intensity + (bout|ID), data = avgVCO2kglbmon, REML=FALSE)
# summary(VCO2kglbmon)
# coef(VCO2kglbmon)
# ranef(VCO2kglbmon)
(summ(VCO2kglbmon)->summVCO2kglbmon)
(BIC(VCO2kglbmon) -> BICVCO2kglbmon)
(summVCO2kglbmon$gvars[,3] -> ICCVCO2kglbmon)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r VCO2kglbmon coefs}
VCO2oncoefs <- as_tibble(coef(VCO2kglbmon)$ID)

VCO2oncoefs <- tibble(demographics, VCO2oncoefs$bout)

write.csv(VCO2oncoefs,"~/R/MBEB-CPET/output/VCO2oncoefs.csv", row.names = TRUE)
```

## VCO2/kg lean body mass OFF TRANSIENT

### Null Model
```{r}
nullmod <- lmer(avgVCO2kglbm ~ 1 + (1|ID), data = avgVCO2kglbmoff, REML = TRUE)
(summ(nullmod) ->summnullVCO2kglbmoff)
(BIC(nullmod) -> BICnullVCO2kglbmoff)
(summnullVCO2kglbmoff$gvars[,3] -> ICCnullVCO2kglbmoff)
```

### Model 2: All interactions

```{r m2 VCO2kglbmoff}
intVCO2kglbmoff <- lmer(avgVCO2kglbm~Gender*Tanner*bout*intensity + (bout|ID) , data = avgVCO2kglbmoff, REML=FALSE)
# summary(intVCO2kglbmoff)
(summ(intVCO2kglbmon)->summintVCO2kglbmon)
(BIC(intVCO2kglbmon) -> BICintVCO2kglbmon)
(summintVCO2kglbmon$gvars[,3] -> ICCintVCO2kglbmon)
# coef(intVCO2kglbmoff)
# fixef(intVCO2kglbmoff)
# ranef(intVCO2kglbmoff)
```

### Model 2C: Some interactions
```{r m2c VCO2kglbmoff}
VCO2kglbmoff <- lmer(avgVCO2kglbm ~ bout + Gender*intensity +Tanner*intensity + (bout|ID),  data = avgVCO2kglbmoff, REML=FALSE)
# summary(VCO2kglbmoff)
# coef(VCO2kglbmoff)
# ranef(VCO2kglbmoff)
(summ(VCO2kglbmoff)->summVCO2kglbmoff)
(BIC(VCO2kglbmoff) -> BICVCO2kglbmoff)
(summVCO2kglbmoff$gvars[,3] -> ICCVCO2kglbmoff)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r VCO2kglbmoff coefs}
VCO2offcoefs <- as_tibble(coef(VCO2kglbmoff)$ID)

VCO2offcoefs <- tibble(demographics, VCO2offcoefs$bout)

write.csv(VCO2offcoefs,"~/R/MBEB-CPET/output/VCO2offcoefs.csv", row.names = TRUE)
```

## RQ On Transient

First, pull out the average on and off transient RQ values for each bout.
```{r compute RQ avg}
avgRQon <- aggregate(ontransbouts$RQ, by=list(bout=ontransbouts$bout, ID = ontransbouts$ID, intensity = ontransbouts$intensity, Gender=ontransbouts$Gender, Tanner=ontransbouts$Tanner), FUN=mean) 
names(avgRQon)[6] <- "avgRQ"

avgRQoff <- aggregate(offtransbouts$RQ, by=list(bout=offtransbouts$bout, ID = offtransbouts$ID, intensity = offtransbouts$intensity, Gender=offtransbouts$Gender, Tanner=offtransbouts$Tanner), FUN=mean)
names(avgRQoff)[6] <- "avgRQ"
```

### Plot the average RQ data distributions.
```{r plot RQ}
#plot the avg ON-transient RQ
ggplot(data=avgRQon, aes(bout, avgRQ, color = intensity)) + geom_point() + ggtitle("On-Transient average RQ rates")

#plot the avg off-transient RQ
ggplot(data=avgRQoff, aes(bout, avgRQ, color = intensity)) + geom_point()+ ggtitle("Off-Transient average RQ rates")

ggplot(data=filter(avgRQon, intensity == "low"), aes(x = bout,y= avgRQ, group = ID)) + geom_line() + ggtitle("Low intensity, Avg RQ for on-transient periods") + ylim(0,2) 
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgRQoff, intensity == "low"), aes(x = bout,y= avgRQ, group = ID)) + geom_line() + ggtitle("Low intensity, Avg RQ for off-transient periods")+  ylim(0,2) 

ggplot(data=filter(avgRQon, intensity == "high"), aes(x = bout,y= avgRQ, group = ID)) + geom_line() + ggtitle("High intensity, Avg RQ for on-transient periods")  + ylim(0,2) 
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgRQoff, intensity == "high"), aes(x = bout,y= avgRQ, group = ID)) + geom_line() + ggtitle("High intensity, Avg RQ for off-transient periods") + ylim(0,2)  
```

### Show xyplots to compare the slopes for each individual based on Gender, Tanner score, intensity
```{r xyplot RQ}
xyplot(avgRQ ~ bout | ID, data = avgRQon, groups = Gender, type = c("p","r"), auto.key = TRUE)

xyplot(avgRQ ~ bout | ID, data = avgRQon, groups = Tanner, type = c("p","r"), auto.key = TRUE)

xyplot(avgRQ ~ bout | ID, data = avgRQon, groups = intensity, type = c("p","r"), auto.key = TRUE)
```

### More visualizations
```{r flexplot RQ}
### categorical variable
flexplot(avgRQ~Gender, data=avgRQon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgRQ~Gender, data=avgRQoff, spread="quartiles", jitter=c(.1, 0))

flexplot(avgRQ~Tanner, data=avgRQon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgRQ~Tanner, data=avgRQoff, spread="quartiles", jitter=c(.1, 0))

### show a straight line, remove standard errors, and specify 2 bins
flexplot(avgRQ~bout + intensity | Gender + Tanner, data=avgRQon, method="lm", se=F, bins=2)

### multivariate relationship
flexplot(avgRQ~bout + intensity | Gender + Tanner, data=avgRQon)
flexplot(avgRQ~bout + Gender | intensity + Tanner, data=avgRQon)
flexplot(avgRQ~bout + Tanner | intensity + Gender, data=avgRQon)
```


### Null Model
```{r}
nullmod <- lmer(avgRQ ~ 1 + (1|ID), data = avgRQon, REML = TRUE)
(summ(nullmod) ->summnullRQon)
(BIC(nullmod) -> BICnullRQon)
(summnullRQon$gvars[,3] -> ICCnullRQon)
```
### Model 1: All interactions

```{r m1 RQon}
intRQon <- lmer(avgRQ~ bout*Gender*Tanner*intensity + (bout|ID)  , data = avgRQon, REML=FALSE)
# summary(intRQon)
(summ(intRQon)->summintRQon)
(BIC(intRQon) -> BICintRQon)
(summintRQon$gvars[,3] -> ICCintRQon)
# coef(intRQon)
# fixef(intRQon)
# ranef(intRQon)
```

### Model 1C: Some interactions

```{r m1C RQon}
RQon <- lmer(avgRQ~ Tanner*intensity + Gender + bout +(bout|ID)  , data = avgRQon, REML=FALSE)
# summary(RQon)
# coef(RQon)
# ranef(RQon)
(summ(RQon)->summRQon)
(BIC(RQon) -> BICRQon)
(summRQon$gvars[,3] -> ICCRQon)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r RQon coefs}
RQoncoefs <- as_tibble(coef(RQon)$ID)

RQoncoefs <- tibble(demographics, RQoncoefs$bout)

write.csv(RQoncoefs,"~/R/MBEB-CPET/output/RQoncoefs.csv", row.names = TRUE)
```

## RQ OFF TRANSIENT

### Null Model
```{r}
nullmod <- lmer(avgRQ ~ 1 + (1|ID), data = avgRQoff, REML = TRUE)
(summ(nullmod) ->summnullRQoff)
(BIC(nullmod) -> BICnullRQoff)
(summnullRQoff$gvars[,3] -> ICCnullRQoff)
```

### Model 2: All interactions

```{r m2 RQoff}
intRQoff <- lmer(avgRQ~ bout*Gender*Tanner*intensity +(bout|ID)  , data = avgRQoff, REML=FALSE)
# summary(intRQoff)
(summ(intRQoff)->summintRQoff)
(BIC(intRQoff) -> BICintRQoff)
(summintRQoff$gvars[,3] -> ICCintRQoff)
# coef(intRQoff)
# fixef(intRQoff)
# ranef(intRQoff)
```

### Model 2C: No interactions
```{r m2c RQoff}
RQoff <- lmer(avgRQ~ bout*intensity + Gender*intensity + Tanner*intensity + (bout|ID)  ,  data = avgRQoff, REML=FALSE)
# summary(RQoff)
# coef(RQoff)
# ranef(RQoff)
(summ(RQoff)->summRQoff)
(BIC(RQoff) -> BICRQoff)
(summRQoff$gvars[,3] -> ICCRQoff)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r RQoff coefs}
RQoffcoefs <- as_tibble(coef(RQoff)$ID)

RQoffcoefs <- tibble(demographics, RQoffcoefs$bout)

write.csv(RQoffcoefs,"~/R/MBEB-CPET/output/RQoffcoefs.csv", row.names = TRUE)
```

## VE/kglbm On Transient

First, pull out the average on and off transient VEkglbm values for each bout.
```{r}
avgVEkglbmon <- aggregate(ontransbouts$'VE/kglbm', by=list(bout=ontransbouts$bout, ID = ontransbouts$ID, intensity = ontransbouts$intensity, Gender=ontransbouts$Gender, Tanner=ontransbouts$Tanner), FUN=mean) 
names(avgVEkglbmon)[6] <- "avgVEkglbm"

avgVEkglbmoff <- aggregate(offtransbouts$'VE/kglbm', by=list(bout=offtransbouts$bout, ID = offtransbouts$ID, intensity = offtransbouts$intensity, Gender=offtransbouts$Gender, Tanner=offtransbouts$Tanner), FUN=mean)
names(avgVEkglbmoff)[6] <- "avgVEkglbm"
```

### Plot the average VEkglbm data distributions.
```{r}
#plot the avg ON-transient VEkglbm
ggplot(data=avgVEkglbmon, aes(bout, avgVEkglbm, color = intensity)) + geom_point() + ggtitle("On-Transient average VEkglbm rates")

#plot the avg off-transient VEkglbm
ggplot(data=avgVEkglbmoff, aes(bout, avgVEkglbm, color = intensity)) + geom_point()+ ggtitle("Off-Transient average VEkglbm rates")

ggplot(data=filter(avgVEkglbmon, intensity == "low"), aes(x = bout,y= avgVEkglbm, group = ID)) + geom_line() + ggtitle("Low intensity, Avg VEkglbm for on-transient periods") + ylim(0,5) 
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgVEkglbmoff, intensity == "low"), aes(x = bout,y= avgVEkglbm, group = ID)) + geom_line() + ggtitle("Low intensity, Avg VEkglbm for off-transient periods")+  ylim(0,5)  

ggplot(data=filter(avgVEkglbmon, intensity == "high"), aes(x = bout,y= avgVEkglbm, group = ID)) + geom_line() + ggtitle("High intensity, Avg VEkglbm for on-transient periods")  + ylim(0,5)  
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgVEkglbmoff, intensity == "high"), aes(x = bout,y= avgVEkglbm, group = ID)) + geom_line() + ggtitle("High intensity, Avg VEkglbm for off-transient periods") + ylim(0,5) 
```

### Show xyplots to compare the slopes for each individual based on Gender, Tanner score, intensity
```{r}
xyplot(avgVEkglbm ~ bout | ID, data = avgVEkglbmon, groups = Gender, type = c("p","r"), auto.key = TRUE)

xyplot(avgVEkglbm ~ bout | ID, data = avgVEkglbmon, groups = Tanner, type = c("p","r"), auto.key = TRUE)

xyplot(avgVEkglbm ~ bout | ID, data = avgVEkglbmon, groups = intensity, type = c("p","r"), auto.key = TRUE)
```

### More visualizations
```{r}
### categorical variable
flexplot(avgVEkglbm~Gender, data=avgVEkglbmon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgVEkglbm~Gender, data=avgVEkglbmoff, spread="quartiles", jitter=c(.1, 0))

flexplot(avgVEkglbm~Tanner, data=avgVEkglbmon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgVEkglbm~Tanner, data=avgVEkglbmoff, spread="quartiles", jitter=c(.1, 0))

### show a straight line, remove standard errors, and specify 2 bins
flexplot(avgVEkglbm~bout + intensity | Gender + Tanner, data=avgVEkglbmon, method="lm", se=F, bins=2)

### multivariate relationship
flexplot(avgVEkglbm~bout + intensity | Gender + Tanner, data=avgVEkglbmon)
flexplot(avgVEkglbm~bout + Gender | intensity + Tanner, data=avgVEkglbmon)
flexplot(avgVEkglbm~bout + Tanner | intensity + Gender, data=avgVEkglbmon)
```


### Null Model
```{r}
nullmod <- lmer(avgVEkglbm ~ 1 + (1|ID), data = avgVEkglbmon, REML = TRUE)
(summ(nullmod) ->summnullVEkglbmon)
(BIC(nullmod) -> BICnullVEkglbmon)
(summnullVEkglbmon$gvars[,3] -> ICCnullVEkglbmon)
```
### Model 1: All interactions

```{r}
intVEkglbmon <- lmer(avgVEkglbm~  bout*intensity*Gender*Tanner +(bout|ID)  , data = avgVEkglbmon, REML=FALSE)
# summary(intVEkglbmon)
(summ(intVEkglbmon)->summintVEkglbmon)
(BIC(intVEkglbmon) -> BICintVEkglbmon)
(summintVEkglbmon$gvars[,3] -> ICCintVEkglbmon)
# coef(intVEkglbmon)
# fixef(intVEkglbmon)
# ranef(intVEkglbmon)
```

### Model 1B: Some interactions

```{r}
VEkglbmon <- lmer(avgVEkglbm~bout + Gender + Tanner*intensity +(bout|ID)  , data = avgVEkglbmon, REML=TRUE)
# summary(VEkglbmon)
# coef(VEkglbmon)
# ranef(VEkglbmon)
(summ(VEkglbmon)->summVEkglbmon)
(BIC(VEkglbmon) -> BICVEkglbmon)
(summVEkglbmon$gvars[,3] -> ICCVEkglbmon)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r}
VEoncoefs <- as_tibble(coef(VEkglbmon)$ID)

VEoncoefs <- tibble(demographics, VEoncoefs$bout)

write.csv(VEoncoefs,"~/R/MBEB-CPET/output/VEoncoefs.csv", row.names = TRUE)
```

## VEkglbm OFF TRANSIENT

### Null Model
```{r}
nullmod <- lmer(avgVEkglbm ~ 1 + (1|ID), data = avgVEkglbmoff, REML = TRUE)
(summ(nullmod) ->summnullVEkglbmoff)
(BIC(nullmod) -> BICnullVEkglbmoff)
(summnullVEkglbmoff$gvars[,3] -> ICCnullVEkglbmoff)
```

### Model 2: All interactions
```{r}
intVEkglbmoff <- lmer(avgVEkglbm~ bout*intensity*Gender*Tanner +(bout|ID) , data = avgVEkglbmoff, REML=FALSE)
# summary(intVEkglbmoff)
(summ(intVEkglbmoff)->summintVEkglbmoff)
(BIC(intVEkglbmoff) -> BICintVEkglbmoff)
(summintVEkglbmoff$gvars[,3] -> ICCintVEkglbmoff)
# coef(intVEkglbmoff)
# fixef(intVEkglbmoff)
# ranef(intVEkglbmoff)
```

### Model 2C: Some interactions
```{r}
VEkglbmoff <- lmer(avgVEkglbm~Gender*intensity + bout*intensity + Tanner*intensity +(bout|ID) , data = avgVEkglbmoff, REML=FALSE)
# summary(VEkglbmoff)
# coef(VEkglbmoff)
# ranef(VEkglbmoff)
(summ(VEkglbmoff)->summVEkglbmoff)
(BIC(VEkglbmoff) -> BICVEkglbmoff)
(summVEkglbmoff$gvars[,3] -> ICCVEkglbmoff)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r}
VEoffcoefs <- as_tibble(coef(VEkglbmoff)$ID)

VEoffcoefs <- tibble(demographics, VEoffcoefs$bout)

write.csv(VEoffcoefs,"~/R/MBEB-CPET/output/VEoffcoefs.csv", row.names = TRUE)
```

## RR On Transient
First, pull out the average on and off transient RR values for each bout.
```{r}
avgRRon <- aggregate(ontransbouts$RR, by=list(bout=ontransbouts$bout, ID = ontransbouts$ID, intensity = ontransbouts$intensity, Gender=ontransbouts$Gender, Tanner=ontransbouts$Tanner), FUN=mean) 
names(avgRRon)[6] <- "avgRR"

avgRRoff <- aggregate(offtransbouts$RR, by=list(bout=offtransbouts$bout, ID = offtransbouts$ID, intensity = offtransbouts$intensity, Gender=offtransbouts$Gender, Tanner=offtransbouts$Tanner), FUN=mean)
names(avgRRoff)[6] <- "avgRR"
```

### Plot the average RR data distributions.
```{r}
#plot the avg ON-transient RR
ggplot(data=avgRRon, aes(bout, avgRR, color = intensity)) + geom_point() + ggtitle("On-Transient average RR rates")

#plot the avg off-transient RR
ggplot(data=avgRRoff, aes(bout, avgRR, color = intensity)) + geom_point()+ ggtitle("Off-Transient average RR rates")

ggplot(data=filter(avgRRon, intensity == "low"), aes(x = bout,y= avgRR, group = ID)) + geom_line() + ggtitle("Low intensity, Avg RR for on-transient periods") + ylim(0,80) 
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgRRoff, intensity == "low"), aes(x = bout,y= avgRR, group = ID)) + geom_line() + ggtitle("Low intensity, Avg RR for off-transient periods")+  ylim(0,80) 

ggplot(data=filter(avgRRon, intensity == "high"), aes(x = bout,y= avgRR, group = ID)) + geom_line() + ggtitle("High intensity, Avg RR for on-transient periods")  + ylim(0,80) 
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgRRoff, intensity == "high"), aes(x = bout,y= avgRR, group = ID)) + geom_line() + ggtitle("High intensity, Avg RR for off-transient periods") + ylim(0,80)  
```

### Show xyplots to compare the slopes for each individual based on Gender, Tanner score, intensity
```{r}
xyplot(avgRR ~ bout | ID, data = avgRRon, groups = Gender, type = c("p","r"), auto.key = TRUE)

xyplot(avgRR ~ bout | ID, data = avgRRon, groups = Tanner, type = c("p","r"), auto.key = TRUE)

xyplot(avgRR ~ bout | ID, data = avgRRon, groups = intensity, type = c("p","r"), auto.key = TRUE)
```

### More visualizations
```{r}
### categorical variable
flexplot(avgRR~Gender, data=avgRRon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgRR~Gender, data=avgRRoff, spread="quartiles", jitter=c(.1, 0))

flexplot(avgRR~Tanner, data=avgRRon, spread="quartiles", jitter=c(.1, 0))
flexplot(avgRR~Tanner, data=avgRRoff, spread="quartiles", jitter=c(.1, 0))

### show a straight line, remoRR standard errors, and specify 2 bins
flexplot(avgRR~bout + intensity | Gender + Tanner, data=avgRRon, method="lm", se=F, bins=2)

### multivariate relationship
flexplot(avgRR~bout + intensity | Gender + Tanner, data=avgRRon)
flexplot(avgRR~bout + Gender | intensity + Tanner, data=avgRRon)
flexplot(avgRR~bout + Tanner | intensity + Gender, data=avgRRon)
```


### Null Model
```{r}
nullmod <- lmer(avgRR ~ 1 + (1|ID), data = avgRRon, REML = TRUE)
(summ(nullmod) ->summnullRRon)
(BIC(nullmod) -> BICnullRRon)
(summnullRRon$gvars[,3] -> ICCnullRRon)
```
### Model 1: All interactions

```{r}
intRRon <- lmer(avgRR~Gender*Tanner*bout*intensity +(bout|ID)  , data = avgRRon, REML=FALSE)
# summary(intRRon)
(summ(intRRon)->summintRRon)
(BIC(intRRon) -> BICintRRon)
(summintRRon$gvars[,3] -> ICCintRRon)
# coef(intRRon)
# fixef(intRRon)
# ranef(intRRon)
```

### Model 1C: Some interactions

```{r}
RRon <- lmer(avgRR~ bout*intensity + Tanner + Gender  + (bout|ID)  , data = avgRRon, REML=FALSE)
# summary(RRon)
# coef(RRon)
# ranef(RRon)
(summ(RRon)->summRRon)
(BIC(RRon) -> BICRRon)
(summRRon$gvars[,3] -> ICCRRon)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r}
RRoncoefs <- as_tibble(coef(RRon)$ID)

RRoncoefs <- tibble(demographics, RRoncoefs$bout)

write.csv(RRoncoefs,"~/R/MBEB-CPET/output/RRoncoefs.csv", row.names = TRUE)
```

## RR OFF TRANSIENT

### Null Model
```{r}
nullmod <- lmer(avgRR ~ 1 + (1|ID), data = avgRRoff, REML = TRUE)
(summ(nullmod) ->summnullRRoff)
(BIC(nullmod) -> BICnullRRoff)
(summnullRRoff$gvars[,3] -> ICCnullRRoff)
```

### Model 2: All interactions

```{r}
intRRoff <- lmer(avgRR~Gender*Tanner*bout*intensity +(bout|ID) , data = avgRRoff, REML=FALSE)
# summary(intRRoff)
(summ(intRRoff)->summintRRoff)
(BIC(intRRoff) -> BICintRRoff)
(summintRRoff$gvars[,3] -> ICCintRRoff)
# coef(intRRoff)
# fixef(intRRoff)
# ranef(intRRoff)
```

### Model 2B: Some interactions
```{r}
RRoff <- lmer(avgRR~ bout*intensity + Gender*Tanner*bout + (bout|ID) , data = avgRRoff, REML=FALSE)
# summary(RRoff)
# coef(RRoff)
# ranef(RRoff)
(summ(RRoff)->summRRoff)
(BIC(RRoff) -> BICRRoff)
(summRRoff$gvars[,3] -> ICCRRoff)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r}
RRoffcoefs <- as_tibble(coef(RRoff)$ID)

RRoffcoefs <- tibble(demographics, RRoffcoefs$bout)

write.csv(RRoffcoefs,"~/R/MBEB-CPET/output/RRoffcoefs.csv", row.names = TRUE)
```

## VE.VCO2 On Transient

First, pull out the average on and off transient VE.VCO2 values for each bout.
```{r}
avgVE.VCO2on <- aggregate(ontransbouts$'VE/VCO2', by=list(bout=ontransbouts$bout, ID = ontransbouts$ID, intensity = ontransbouts$intensity, Gender=ontransbouts$Gender, Tanner=ontransbouts$Tanner), FUN=mean) 
names(avgVE.VCO2on)[6] <- "avgVE.VCO2"

avgVE.VCO2off <- aggregate(offtransbouts$'VE/VCO2', by=list(bout=offtransbouts$bout, ID = offtransbouts$ID, intensity = offtransbouts$intensity, Gender=offtransbouts$Gender, Tanner=offtransbouts$Tanner), FUN=mean)
names(avgVE.VCO2off)[6] <- "avgVE.VCO2"
```

### Plot the average VE/VCO2 data distributions.
```{r}
#plot the avg ON-transient VE/VCO2
ggplot(data=avgVE.VCO2on, aes(bout, avgVE.VCO2, color = intensity)) + geom_point() + ggtitle("On-Transient average VE/VCO2 rates")

#plot the avg off-transient VE/VCO2
ggplot(data=avgVE.VCO2off, aes(bout, avgVE.VCO2, color = intensity)) + geom_point()+ ggtitle("Off-Transient average VE/VCO2 rates")

ggplot(data=filter(avgVE.VCO2on, intensity == "low"), aes(x = bout,y= avgVE.VCO2, group = ID)) + geom_line() + ggtitle("Low intensity, Avg VE/VCO2 for on-transient periods")+ ylim(20,80)
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgVE.VCO2off, intensity == "low"), aes(x = bout,y= avgVE.VCO2, group = ID)) + geom_line() + ggtitle("Low intensity, Avg VE/VCO2 for off-transient periods")+ ylim(20,80)

ggplot(data=filter(avgVE.VCO2on, intensity == "high"), aes(x = bout,y= avgVE.VCO2, group = ID)) + geom_line() + ggtitle("High intensity, Avg VE/VCO2 for on-transient periods")+ ylim(20,80)
# + geom_abline(intercept = 139, slope=7.6,color = "red", linetype="dashed", size = 1.7)

ggplot(data=filter(avgVE.VCO2off, intensity == "high"), aes(x = bout,y= avgVE.VCO2, group = ID)) + geom_line() + ggtitle("High intensity, Avg VE/VCO2 for off-transient periods") + ylim(20,80)
```

### Show xyplots to compare the slopes for each individual based on Gender, Tanner score, intensity
```{r}
xyplot(avgVE.VCO2 ~ bout | ID, data = avgVE.VCO2on, groups = Gender, type = c("p","r"), auto.key = TRUE)

xyplot(avgVE.VCO2 ~ bout | ID, data = avgVE.VCO2on, groups = Tanner, type = c("p","r"), auto.key = TRUE)

xyplot(avgVE.VCO2 ~ bout | ID, data = avgVE.VCO2on, groups = intensity, type = c("p","r"), auto.key = TRUE)
```

### More visualizations
```{r}
### categorical variable
flexplot(avgVE.VCO2~Gender, data=avgVE.VCO2on, spread="quartiles", jitter=c(.1, 0))
flexplot(avgVE.VCO2~Gender, data=avgVE.VCO2off, spread="quartiles", jitter=c(.1, 0))

flexplot(avgVE.VCO2~Tanner, data=avgVE.VCO2on, spread="quartiles", jitter=c(.1, 0))
flexplot(avgVE.VCO2~Tanner, data=avgVE.VCO2off, spread="quartiles", jitter=c(.1, 0))

### show a straight line, remove standard errors, and specify 2 bins
flexplot(avgVE.VCO2~bout + intensity | Gender + Tanner, data=avgVE.VCO2on, method="lm", se=F, bins=2)

### multivariate relationship
flexplot(avgVE.VCO2~bout + intensity | Gender + Tanner, data=avgVE.VCO2on)
flexplot(avgVE.VCO2~bout + Gender | intensity + Tanner, data=avgVE.VCO2on)
flexplot(avgVE.VCO2~bout + Tanner | intensity + Gender, data=avgVE.VCO2on)
```


### Null Model
```{r}
nullmod <- lmer(avgVE.VCO2 ~ 1 + (1|ID), data = avgVE.VCO2on, REML = TRUE)
(summ(nullmod) ->summnullVE.VCO2on)
(BIC(nullmod) -> BICnullVE.VCO2on)
(summnullVE.VCO2on$gvars[,3] -> ICCnullVE.VCO2on)
```
### Model 1: All interactions

```{r}
intVE.VCO2on <- lmer(avgVE.VCO2~Gender*Tanner*bout*intensity +(bout|ID)  , data = avgVE.VCO2on, REML=FALSE)
# summary(intVE.VCO2on)
(summ(intVE.VCO2on)->summintVE.VCO2on)
(BIC(intVE.VCO2on) -> BICintVE.VCO2on)
(summintVE.VCO2on$gvars[,3] -> ICCintVE.VCO2on)
# coef(intVE.VCO2on)
# fixef(intVE.VCO2on)
# ranef(intVE.VCO2on)
```

### Model 1C: Some interactions
```{r}
VE.VCO2on <- lmer(avgVE.VCO2~ bout*intensity + Tanner*intensity + Gender  + (bout|ID)  , data = avgVE.VCO2on, REML=FALSE)
# summary(VE.VCO2on)
# coef(VE.VCO2on)
# ranef(VE.VCO2on)
(summ(VE.VCO2on)->summVE.VCO2on)
(BIC(VE.VCO2on) -> BICVE.VCO2on)
(summVE.VCO2on$gvars[,3] -> ICCVE.VCO2on)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r}
VE.VCO2oncoefs <- as_tibble(coef(VE.VCO2on)$ID)

VE.VCO2oncoefs <- tibble(demographics, VE.VCO2oncoefs$bout)

write.csv(VE.VCO2oncoefs,"~/R/MBEB-CPET/output/VE.VCO2oncoefs.csv", row.names = TRUE)
```

## VE.VCO2 OFF TRANSIENT

### Null Model
```{r}
nullmod <- lmer(avgVE.VCO2 ~ 1 + (1|ID), data = avgVE.VCO2off, REML = TRUE)
(summ(nullmod) ->summnullVE.VCO2off)
(BIC(nullmod) -> BICnullVE.VCO2off)
(summnullVE.VCO2off$gvars[,3] -> ICCnullVE.VCO2off)
```

### Model 2: All interactions

```{r}
intVE.VCO2off <- lmer(avgVE.VCO2~Gender*Tanner*bout*intensity +(bout|ID) , data = avgVE.VCO2off, REML=FALSE)
# summary(intVE.VCO2off)
(summ(intVE.VCO2off)->summintVE.VCO2off)
(BIC(intVE.VCO2off) -> BICintVE.VCO2off)
(summintVE.VCO2off$gvars[,3] -> ICCintVE.VCO2off)
# coef(intVE.VCO2off)
# fixef(intVE.VCO2off)
# ranef(intVE.VCO2off)
```

### Model 2C: Some interactions
```{r}
VE.VCO2off <- lmer(avgVE.VCO2~ bout + Gender + Tanner* intensity + (bout|ID) , data = avgVE.VCO2off, REML=TRUE)
# summary(VE.VCO2off)
# coef(VE.VCO2off)
# ranef(VE.VCO2off)
(summ(VE.VCO2off)->summVE.VCO2off)
(BIC(VE.VCO2off) -> BICVE.VCO2off)
(summVE.VCO2off$gvars[,3] -> ICCVE.VCO2off)
```

### Create a tibble of model coefficients by ID.
This generates a table of individualized coefficients for each subject, which includes fixed effects + random effects. These will be used for analysis of group averages.

```{r}
VE.VCO2offcoefs <- as_tibble(coef(VE.VCO2off)$ID)

VE.VCO2offcoefs <- tibble(demographics, VE.VCO2offcoefs$bout)

write.csv(VE.VCO2offcoefs,"~/R/MBEB-CPET/output/VE.VCO2offcoefs.csv", row.names = TRUE)
```

# Predicted Values

## Predict and visualize the linear models.

https://strengejacke.github.io/ggeffects/articles/introduction_randomeffects.html

When type = "random", the predicted values are still on the population-level. However, the random effect variances are taken into account, meaning that the intervals are actually prediction intervals and become larger. More technically speaking, type = "random" accounts for the uncertainty of the fixed effects conditional on the estimates of the random-effect variances and conditional modes (BLUPs).

The random-effect variance is the mean random-effect variance. Calculation is based on the proposal from Johnson et al. 2014, which is also implemented in functions like performance::r2() or insight::get_variance() to get r-squared values or random effect variances for mixed models with more complex random effects structures.

As can be seen, compared to the previous example with type = "fixed", predicted values are identical (both on the population-level). However, standard errors, and thus the resulting confidence (or prediction) intervals are much larger .

```{r}
# Another way to do this is with plot_model:  
# plot_model(HRon, type = "pred", terms = c("bout[1,2,3,4,5]", "Tanner", "intensity"))

dat.HRon <- ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender","Tanner","intensity"), type = "random")
plot(dat.HRon, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")
write.csv(dat.HRon,"~/R/MBEB-CPET/output/dat.HRon.csv", row.names = FALSE)

dat.HRoff <- ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.HRoff,"~/R/MBEB-CPET/output/dat.HRoff.csv", row.names = FALSE)
plot(dat.HRoff, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.VO2KGLBMon <- ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.VO2KGLBMon,"~/R/MBEB-CPET/output/dat.VO2KGLBMon.csv", row.names = FALSE)
plot(dat.VO2KGLBMon, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.VO2KGLBMoff <- ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.VO2KGLBMoff,"~/R/MBEB-CPET/output/dat.VO2KGLBMoff.csv", row.names = FALSE)
plot(dat.VO2KGLBMoff, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.VCO2kglbmon <- ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.VCO2kglbmon,"~/R/MBEB-CPET/output/dat.VCO2kglbmon.csv", row.names = FALSE)
plot(dat.VCO2kglbmon, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.VCO2kglbmoff <- ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.VCO2kglbmoff,"~/R/MBEB-CPET/output/dat.VCO2kglbmoff.csv", row.names = FALSE)
plot(dat.VCO2kglbmoff, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.RQon <- ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.RQon,"~/R/MBEB-CPET/output/dat.RQon.csv", row.names = FALSE)
plot(dat.RQon, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.RQoff <- ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.RQoff,"~/R/MBEB-CPET/output/dat.RQoff.csv", row.names = FALSE)
plot(dat.RQoff, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.VEkglbmon <- ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.VEkglbmon,"~/R/MBEB-CPET/output/dat.VEkglbmon.csv", row.names = FALSE)
plot(dat.VEkglbmon, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.VEkglbmoff <- ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.VEkglbmoff,"~/R/MBEB-CPET/output/dat.VEkglbmoff.csv", row.names = FALSE)
plot(dat.VEkglbmoff, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.RRon <- ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.RRon,"~/R/MBEB-CPET/output/dat.RRon.csv", row.names = FALSE)
plot(dat.RRon, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.RRoff <- ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.RRoff,"~/R/MBEB-CPET/output/dat.RRoff.csv", row.names = FALSE)
plot(dat.RRoff, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.VE.VCO2on <- ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.VE.VCO2on,"~/R/MBEB-CPET/output/dat.VE.VCO2on.csv", row.names = FALSE)
plot(dat.VE.VCO2on, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")

dat.VE.VCO2off <- ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender", "Tanner", "intensity"))
write.csv(dat.VE.VCO2off,"~/R/MBEB-CPET/output/dat.VE.VCO2off.csv", row.names = FALSE)
plot(dat.VE.VCO2off, ci.style = "dot", add.data = TRUE, use.theme = T, connect.lines = T,residuals = TRUE, residuals.line = FALSE, dot.alpha = 0.5, dot.size = 3, jitter = NULL, collapse.group = "intensity")
```

## Individual prediction plots

To produce plots of the estimated marginal means (from the model) compared to the raw data at each combination of levels:

### HRon
```{r}
CPET <- 'HRon'
```

MALES
```{r}
grouping <-  'MEH'

#raw data of MEH
MEH <- filter(avgHRon, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgHR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean HR: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MEL'

#raw data of MEL
MEL <- filter(avgHRon, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgHR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean HR: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLL'

#raw data of MLL
MLL <- filter(avgHRon, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgHR'


#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean HR: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLH'

#raw data of MLH
MLH <- filter(avgHRon, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean HR: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
grouping <-  'FEH'

#raw data of FEH
FEH <- filter(avgHRon, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgHR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean HR: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FEL'

#raw data of FEL
FEL <- filter(avgHRon, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgHR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean HR: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLL'

#raw data of FLL
FLL <- filter(avgHRon, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean HR: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLH'

#raw data of FLH
FLH <- filter(avgHRon, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(HRon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean HR: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### HRoff
```{r}
CPET <- 'HRoff'
```

MALES
```{r}
#raw data of MEH
MEH <- filter(avgHRoff, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgHR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean HR: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MEL
MEL <- filter(avgHRoff, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgHR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean HR: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLL
MLL <- filter(avgHRoff, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean HR: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLH
MLH <- filter(avgHRoff, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean HR: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
#raw data of FEH
FEH <- filter(avgHRoff, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgHR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean HR: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FEL
FEL <- filter(avgHRoff, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgHR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean HR: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLL
FLL <- filter(avgHRoff, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean HR: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLH
FLH <- filter(avgHRoff, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(HRoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgHR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgHR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgHR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgHR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean HR: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### VO2/kg on
```{r}
CPET <- 'VO2kg'
```

MALES
```{r}
grouping <- "MEH"

#raw data of MEH
MEH <- filter(avgVO2kglbmon, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "MEL"

#raw data of MEL
MEL <- filter(avgVO2kglbmon, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "MLL"

#raw data of MLL
MLL <- filter(avgVO2kglbmon, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "MLH"

#raw data of MLH
MLH <- filter(avgVO2kglbmon, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
grouping <- "FEH"

#raw data of FEH
FEH <- filter(avgVO2kglbmon, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "FEL"

#raw data of FEL
FEL <- filter(avgVO2kglbmon, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "FLL"

#raw data of FLL
FLL <- filter(avgVO2kglbmon, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "FLH"
#raw data of FLH
FLH <- filter(avgVO2kglbmon, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(VO2KGLBMon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### VO2/kg off
```{r}
CPET <- 'VO2kg'
```

MALES
```{r}
grouping <- "MEH"

#raw data of MEH
MEH <- filter(avgVO2kglbmoff, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "MEL"

#raw data of MEL
MEL <- filter(avgVO2kglbmoff, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "MLL"

#raw data of MLL
MLL <- filter(avgVO2kglbmoff, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "MLH"

#raw data of MLH
MLH <- filter(avgVO2kglbmoff, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
grouping <- "FEH"

#raw data of FEH
FEH <- filter(avgVO2kglbmoff, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "FEL"

#raw data of FEL
FEL <- filter(avgVO2kglbmoff, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "FLL"

#raw data of FLL
FLL <- filter(avgVO2kglbmoff, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <- "FLH"
#raw data of FLH
FLH <- filter(avgVO2kglbmoff, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(VO2KGLBMoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgVO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VO2/kg Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```







```{r Plot the fixed effects estimates}
# Currently not used for this analysis.

# plot_summs(VCO2on, VCO2off, scale = TRUE, 
#            # inner_ci_level = .95, 
#            plot.distributions = F)
```


### VCO2/kg on
```{r}
CPET <- 'VCO2on'
```

MALES
```{r}
grouping <-  'MEH'

#raw data of MEH
MEH <- filter(avgVCO2kglbmon, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVCO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VCO2kglbm: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MEL'

#raw data of MEL
MEL <- filter(avgVCO2kglbmon, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVCO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VCO2kglbm: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLL'

#raw data of MLL
MLL <- filter(avgVCO2kglbmon, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgVCO2kglbm'


#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VCO2kglbm: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLH'

#raw data of MLH
MLH <- filter(avgVCO2kglbmon, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VCO2kglbm: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
grouping <-  'FEH'

#raw data of FEH
FEH <- filter(avgVCO2kglbmon, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVCO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VCO2kglbm: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FEL'

#raw data of FEL
FEL <- filter(avgVCO2kglbmon, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVCO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VCO2kglbm: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLL'

#raw data of FLL
FLL <- filter(avgVCO2kglbmon, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VCO2kglbm: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLH'

#raw data of FLH
FLH <- filter(avgVCO2kglbmon, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(VCO2kglbmon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VCO2kglbm: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### VCO2/kg off
```{r}
CPET <- 'VCO2off'
```

MALES
```{r}
#raw data of MEH
MEH <- filter(avgVCO2kglbmoff, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVCO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VCO2kglbm: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MEL
MEL <- filter(avgVCO2kglbmoff, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVCO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VCO2kglbm: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLL
MLL <- filter(avgVCO2kglbmoff, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VCO2kglbm: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLH
MLH <- filter(avgVCO2kglbmoff, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VCO2kglbm: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
#raw data of FEH
FEH <- filter(avgVCO2kglbmoff, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVCO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VCO2kglbm: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FEL
FEL <- filter(avgVCO2kglbmoff, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVCO2kglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VCO2kglbm: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLL
FLL <- filter(avgVCO2kglbmoff, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VCO2kglbm: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLH
FLH <- filter(avgVCO2kglbmoff, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(VCO2kglbmoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgVCO2kglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVCO2kglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVCO2kglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VCO2kglbm: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### RQon
```{r}
CPET <- 'RQon'
```

MALES
```{r}
grouping <-  'MEH'

#raw data of MEH
MEH <- filter(avgRQon, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgRQ, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RQ: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MEL'

#raw data of MEL
MEL <- filter(avgRQon, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgRQ, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RQ: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLL'

#raw data of MLL
MLL <- filter(avgRQon, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgRQ'


#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RQ: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLH'

#raw data of MLH
MLH <- filter(avgRQon, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RQ: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
grouping <-  'FEH'

#raw data of FEH
FEH <- filter(avgRQon, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgRQ, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RQ: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FEL'

#raw data of FEL
FEL <- filter(avgRQon, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgRQ, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RQ: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLL'

#raw data of FLL
FLL <- filter(avgRQon, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RQ: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLH'

#raw data of FLH
FLH <- filter(avgRQon, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(RQon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RQ: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### RQoff
```{r}
CPET <- 'RQoff'
```

MALES
```{r}
#raw data of MEH
MEH <- filter(avgRQoff, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgRQ, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RQ: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MEL
MEL <- filter(avgRQoff, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgRQ, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RQ: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLL
MLL <- filter(avgRQoff, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RQ: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLH
MLH <- filter(avgRQoff, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RQ: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
#raw data of FEH
FEH <- filter(avgRQoff, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgRQ, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RQ: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FEL
FEL <- filter(avgRQoff, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgRQ, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RQ: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLL
FLL <- filter(avgRQoff, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RQ: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLH
FLH <- filter(avgRQoff, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(RQoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgRQ'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgRQ, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRQ, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RQ: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### VEon
```{r}
CPET <- 'VEon'
```

MALES
```{r}
grouping <-  'MEH'

#raw data of MEH
MEH <- filter(avgVEkglbmon, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVEkglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VEkglbm: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MEL'

#raw data of MEL
MEL <- filter(avgVEkglbmon, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVEkglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VEkglbm: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLL'

#raw data of MLL
MLL <- filter(avgVEkglbmon, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgVEkglbm'


#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VEkglbm: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLH'

#raw data of MLH
MLH <- filter(avgVEkglbmon, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VEkglbm: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
grouping <-  'FEH'

#raw data of FEH
FEH <- filter(avgVEkglbmon, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVEkglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VEkglbm: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FEL'

#raw data of FEL
FEL <- filter(avgVEkglbmon, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVEkglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VEkglbm: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLL'

#raw data of FLL
FLL <- filter(avgVEkglbmon, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VEkglbm: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLH'

#raw data of FLH
FLH <- filter(avgVEkglbmon, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(VEkglbmon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VEkglbm: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### VEoff
```{r}
CPET <- 'VEoff'
```

MALES
```{r}
#raw data of MEH
MEH <- filter(avgVEkglbmoff, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVEkglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VEkglbm: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MEL
MEL <- filter(avgVEkglbmoff, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVEkglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VEkglbm: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLL
MLL <- filter(avgVEkglbmoff, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VEkglbm: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLH
MLH <- filter(avgVEkglbmoff, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VEkglbm: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
#raw data of FEH
FEH <- filter(avgVEkglbmoff, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVEkglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VEkglbm: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FEL
FEL <- filter(avgVEkglbmoff, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVEkglbm, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VEkglbm: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLL
FLL <- filter(avgVEkglbmoff, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VEkglbm: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLH
FLH <- filter(avgVEkglbmoff, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(VEkglbmoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgVEkglbm'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVEkglbm, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVEkglbm, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VEkglbm: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### RRon
```{r}
CPET <- 'RRon'
```

MALES
```{r}
grouping <-  'MEH'

#raw data of MEH
MEH <- filter(avgRRon, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgRR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RR: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MEL'

#raw data of MEL
MEL <- filter(avgRRon, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgRR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RR: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLL'

#raw data of MLL
MLL <- filter(avgRRon, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgRR'


#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RR: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLH'

#raw data of MLH
MLH <- filter(avgRRon, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RR: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
grouping <-  'FEH'

#raw data of FEH
FEH <- filter(avgRRon, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgRR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RR: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FEL'

#raw data of FEL
FEL <- filter(avgRRon, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgRR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RR: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLL'

#raw data of FLL
FLL <- filter(avgRRon, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RR: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLH'

#raw data of FLH
FLH <- filter(avgRRon, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(RRon, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean RR: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### RRoff
```{r}
CPET <- 'RRoff'
```

MALES
```{r}
#raw data of MEH
MEH <- filter(avgRRoff, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgRR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RR: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MEL
MEL <- filter(avgRRoff, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgRR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RR: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLL
MLL <- filter(avgRRoff, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RR: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLH
MLH <- filter(avgRRoff, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RR: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
#raw data of FEH
FEH <- filter(avgRRoff, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgRR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RR: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FEL
FEL <- filter(avgRRoff, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgRR, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RR: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLL
FLL <- filter(avgRRoff, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RR: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLH
FLH <- filter(avgRRoff, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(RRoff, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgRR'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgRR, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgRR, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgRR, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean RR: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### VE.VCO2on
```{r}
CPET <- 'VE.VCO2on'
```

MALES
```{r}
grouping <-  'MEH'

#raw data of MEH
MEH <- filter(avgVE.VCO2on, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVE.VCO2, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VE.VCO2: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MEL'

#raw data of MEL
MEL <- filter(avgVE.VCO2on, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVE.VCO2, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VE.VCO2: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLL'

#raw data of MLL
MLL <- filter(avgVE.VCO2on, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgVE.VCO2'


#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VE.VCO2: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'MLH'

#raw data of MLH
MLH <- filter(avgVE.VCO2on, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VE.VCO2: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
grouping <-  'FEH'

#raw data of FEH
FEH <- filter(avgVE.VCO2on, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVE.VCO2, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VE.VCO2: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FEL'

#raw data of FEL
FEL <- filter(avgVE.VCO2on, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVE.VCO2, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VE.VCO2: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLL'

#raw data of FLL
FLL <- filter(avgVE.VCO2on, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VE.VCO2: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
grouping <-  'FLH'

#raw data of FLH
FLH <- filter(avgVE.VCO2on, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(VE.VCO2on, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("On-Transient Mean VE.VCO2: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

### VE.VCO2off
```{r}
CPET <- 'VE.VCO2off'
```

MALES
```{r}
#raw data of MEH
MEH <- filter(avgVE.VCO2off, Gender == "MALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MEH
dat.MEH <- as.data.frame(ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.MEH)[1] <- 'bout'
names(dat.MEH)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEH) + 
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVE.VCO2, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VE.VCO2: Early Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MEL
MEL <- filter(avgVE.VCO2off, Gender == "MALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MEL
dat.MEL <- as.data.frame(ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.MEL)[1] <- 'bout'
names(dat.MEL)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MEL) + 
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MEL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = MEH, aes(x = bout, y = avgVE.VCO2, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VE.VCO2: Early Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLL
MLL <- filter(avgVE.VCO2off, Gender == "MALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of MLL
dat.MLL <- as.data.frame(ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.MLL)[1] <- 'bout'
names(dat.MLL)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLL) + 
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VE.VCO2: Late Puberty Male, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of MLH
MLH <- filter(avgVE.VCO2off, Gender == "MALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of MLH
dat.MLH <- as.data.frame(ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender[MALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.MLH)[1] <- 'bout'
names(dat.MLH)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.MLH) + 
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = MLH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VE.VCO2: Late Puberty Male, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```

FEMALES
```{r}
#raw data of FEH
FEH <- filter(avgVE.VCO2off, Gender == "FEMALE", Tanner == "Early", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FEH
dat.FEH <- as.data.frame(ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[high]"), type = "random"))
names(dat.FEH)[1] <- 'bout'
names(dat.FEH)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEH) + 
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVE.VCO2, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VE.VCO2: Early Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FEL
FEL <- filter(avgVE.VCO2off, Gender == "FEMALE", Tanner == "Early", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FEL
dat.FEL <- as.data.frame(ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Early]","intensity[low]"), type = "random"))
names(dat.FEL)[1] <- 'bout'
names(dat.FEL)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FEL) + 
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FEL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  # geom_point(data = FEH, aes(x = bout, y = avgVE.VCO2, color = 'black'), alpha = 0.5) +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VE.VCO2: Early Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLL
FLL <- filter(avgVE.VCO2off, Gender == "FEMALE", Tanner == "Late", intensity == "low", bout %in% c(1,2,3,4,5))

#emmeans of FLL
dat.FLL <- as.data.frame(ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[low]"), type = "random"))
names(dat.FLL)[1] <- 'bout'
names(dat.FLL)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLL) + 
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLL, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VE.VCO2: Late Puberty FEMALE, Low intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```
```{r}
#raw data of FLH
FLH <- filter(avgVE.VCO2off, Gender == "FEMALE", Tanner == "Late", intensity == "high", bout %in% c(1,2,3,4,5))

#emmeans of FLH
dat.FLH <- as.data.frame(ggpredict(VE.VCO2off, terms = c("bout[1,2,3,4,5]","Gender[FEMALE]","Tanner[Late]","intensity[high]"), type = "random"))
names(dat.FLH)[1] <- 'bout'
names(dat.FLH)[2] <- 'avgVE.VCO2'

#save the plot
jpeg(file= here("output/meanplots",paste0(CPET,grouping,"means",".jpeg"))
       , width = 800, height = 500)

ggplot(data = dat.FLH) + 
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun = mean, geom = "point")+
  stat_summary(data = FLH, mapping = aes(x = bout, y = avgVE.VCO2, color = "black"), fun.data = mean_se, geom = "errorbar") +
  geom_point(mapping = aes(x = bout, y = avgVE.VCO2, color = 'red'), pch = 1, size = 4) +
  theme_bw() + 
  ggtitle("Off-Transient Mean VE.VCO2: Late Puberty FEMALE, High intensity") +
  scale_colour_manual(name = "data", values = c('red'='red', 'black'='black'),labels =c('Raw Data (Std Error)','Est Marginal Mean'))

dev.off()
```


# Printing the model results as tables
## Tab_model version

 Adjust file name in the tab_model function to specify html save location.
```{r}
allmodels <- c(HRon, HRoff, VO2KGLBMon,VO2KGLBMoff, VCO2kglbmon,VCO2kglbmoff,RQon,RQoff,VEkglbmon,VEkglbmoff,RRon,RRoff,VE.VCO2on, VE.VCO2off)

tab_model(allmodels, 
          show.reflvl = F, 
          auto.label=TRUE, 
          show.fstat = TRUE,
          dv.labels = c("HR (on)", "HR (off)", "VO2/kg (on)", "VO2/kg (off)", "VCO2/kg (on)", "VCO2/kg (off)", "RQ (on)", "RQ (off)", "VE/kg (on)", "VE/kg (off)", "RR (on)", "RR (off)", "VE/VCO2 (on)", "VE/VCO2 (off)"),
          CSS = css_theme("cells")
          # ,file = "C:/Users/__.html"
          )
```

## Individual tab_models
```{r}
HRmodels <- c(HRon, HRoff)
tab_model(HRmodels, show.reflvl = F, auto.label=TRUE 
          # ,prefix.labels ="varname"
          , dv.labels = c("HR (exercise)", "HR (rest)")
          , CSS = css_theme("cells")
          ,file = "~/R/MBEB-CPET/output/HRmodels.html"
          )

# VO2KGmodels <- c(VO2KGon, VO2KGoff)
# tab_model(VO2KGmodels, show.reflvl = F, auto.label=TRUE 
#           # ,prefix.labels ="varname"
#           , dv.labels = c("VO2/kg (exercise)", "VO2/kg (rest)")
#           , CSS = css_theme("cells")
#           ,file = "~/R/MBEB-CPET/output/HRmodels.html"
#           )

VO2KGLBMmodels <- c(VO2KGLBMon, VO2KGLBMoff)
tab_model(VO2KGLBMmodels, show.reflvl = F, auto.label=TRUE 
          # ,prefix.labels ="varname"
          , dv.labels = c("VO2/kg (exercise)", "VO2/kg (rest)")
          , CSS = css_theme("cells")
          ,file = "~/R/MBEB-CPET/output/VO2models.html"
          )

# VCO2models <- c(VCO2on, VCO2off)
# tab_model(VCO2models, show.reflvl = F, auto.label=TRUE 
#           # ,prefix.labels ="varname"
#           , dv.labels = c("VCO2 (exercise)", "VCO2 (rest)")
#           , CSS = css_theme("cells")
#           ,file = "~/R/MBEB-CPET/output/HRmodels.html"
#           )

VCO2kglbmmodels <- c(VCO2kglbmon, VCO2kglbmoff)
tab_model(VCO2kglbmmodels, show.reflvl = F, auto.label=TRUE 
          # ,prefix.labels ="varname"
          , dv.labels = c("VCO2/kg (exercise)", "VCO2/kg (rest)")
          , CSS = css_theme("cells")
          ,file = "~/R/MBEB-CPET/output/VCO2models.html"
          )

RQmodels <- c(RQon, RQoff)
tab_model(RQmodels, show.reflvl = F, auto.label=TRUE 
          # ,prefix.labels ="varname"
          , dv.labels = c("RQ (exercise)", "RQ (rest)")
          , CSS = css_theme("cells")
          ,file = "~/R/MBEB-CPET/output/RQmodels.html"
          )

# VEmodels <- c(VEon, VEoff)
# tab_model(VEmodels, show.reflvl = F, auto.label=TRUE 
#           # ,prefix.labels ="varname"
#           , dv.labels = c("VE (exercise)", "VE (rest)")
#           , CSS = css_theme("cells")
#           ,file = "~/R/MBEB-CPET/output/VEmodels.html"
#           )

VEkglbmmodels <- c(VEkglbmon, VEkglbmoff)
tab_model(VEkglbmmodels, show.reflvl = F, auto.label=TRUE 
          # ,prefix.labels ="varname"
          , dv.labels = c("VE/kg (exercise)", "VE/kg (rest)")
          , CSS = css_theme("cells")
          ,file = "~/R/MBEB-CPET/output/VEmodels.html"
          )

RRmodels <- c(RRon, RRoff)
tab_model(RRmodels, show.reflvl = F, auto.label=TRUE 
          # ,prefix.labels ="varname"
          , dv.labels = c("RR (exercise)", "RR (rest)")
          , CSS = css_theme("cells")
          ,file = "~/R/MBEB-CPET/output/RRmodels.html"
          )

VE.VCO2models <- c(VE.VCO2on, VE.VCO2off)
tab_model(VE.VCO2models, show.reflvl = F, auto.label=TRUE 
          # ,prefix.labels ="varname"
          , dv.labels = c("VE/VCO2 (exercise)", "VE/VCO2 (rest)")
          , CSS = css_theme("cells")
          ,file = "~/R/MBEB-CPET/output/VE.VCO2models.html"
          )
```

# Residuals analysis
Three plots can be generated:

1. A histogram of the residuals for each model against its original data.

2. Distribution of the residuals for the random effect of ‘bout’ in the model. Measure of the conditional variance.

3. A scatterplot of the residuals. Indicates normal distribution.

```{r}
HRonresiduals <- resid(HRon)
summary(HRonresiduals) #a summary of the residuals for this model
hist(HRonresiduals) # a histogram of the residuals distribution
print(dotplot(ranef(HRon,condVar=TRUE))) # a dotplot of the random effects residuals
plot(HRon) # a scatter plot of the residuals
```
```{r}
HRoffresiduals <- resid(HRoff)
summary(HRoffresiduals)
hist(HRoffresiduals)
print(dotplot(ranef(HRoff,condVar=TRUE)))
plot(HRoff)
```
```{r}
VO2KGLBMonresiduals <- resid(VO2KGLBMon)
summary(VO2KGLBMonresiduals)
hist(VO2KGLBMonresiduals)
print(dotplot(ranef(VO2KGLBMon,condVar=TRUE)))
plot(VO2KGLBMon)
```
```{r}
VO2KGLBMoffresiduals <- resid(VO2KGLBMoff)
summary(VO2KGLBMoffresiduals)
hist(VO2KGLBMoffresiduals)
print(dotplot(ranef(VO2KGLBMoff,condVar=TRUE)))
plot(VO2KGLBMoff)
```
```{r}
VCO2kglbmonresiduals <- resid(VCO2kglbmon)
summary(VCO2kglbmonresiduals)
hist(VCO2kglbmonresiduals)
print(dotplot(ranef(VCO2kglbmon,condVar=TRUE)))
plot(VCO2kglbmon)
```
```{r}
VCO2kglbmoffresiduals <- resid(VCO2kglbmoff)
summary(VCO2kglbmoffresiduals)
hist(VCO2kglbmoffresiduals)
print(dotplot(ranef(VCO2kglbmoff,condVar=TRUE)))
plot(VCO2kglbmoff)
```
```{r}
VEkglbmonresiduals <- resid(VEkglbmon)
summary(VEkglbmonresiduals)
hist(VEkglbmonresiduals)
print(dotplot(ranef(VEkglbmon,condVar=TRUE)))
plot(VEkglbmon)
```
```{r}
VEkglbmoffresiduals <- resid(VEkglbmoff)
summary(VEkglbmoffresiduals)
hist(VEkglbmoffresiduals)
print(dotplot(ranef(VEkglbmoff,condVar=TRUE)))
plot(VEkglbmoff)
```
```{r}
RQonresiduals <- resid(RQon)
summary(RQonresiduals)
hist(RQonresiduals)
print(dotplot(ranef(RQon,condVar=TRUE)))
plot(RQon)
```
```{r}
RQoffresiduals <- resid(RQoff)
summary(RQoffresiduals)
hist(RQoffresiduals)
print(dotplot(ranef(RQoff,condVar=TRUE)))
plot(RQoff)
```
```{r}
RRonresiduals <- resid(RRon)
summary(RRonresiduals)
hist(RRonresiduals)
print(dotplot(ranef(RRon,condVar=TRUE)))
plot(RRon)
```
```{r}
RRoffresiduals <- resid(RRoff)
summary(RRoffresiduals)
hist(RRoffresiduals)
print(dotplot(ranef(RRoff,condVar=TRUE)))
plot(RRoff)
```
```{r}
VE.VCO2onresiduals <- resid(VE.VCO2on)
summary(VE.VCO2onresiduals)
hist(VE.VCO2onresiduals)
print(dotplot(ranef(VE.VCO2on,condVar=TRUE)))
plot(VE.VCO2on)
```
```{r}
VE.VCO2offresiduals <- resid(VE.VCO2off)
plot(resid(VE.VCO2off))
summary(VE.VCO2offresiduals)
hist(VE.VCO2offresiduals)
print(dotplot(ranef(VE.VCO2off,condVar=TRUE)))
plot(VE.VCO2off)
```
